V1298~Tau with TESS: Updated Ephemerides, Radii, and Period Constraints from a Second Transit of V1298~Tau~e

### 2021-11-11 src/ms.tex
all da last minute stuff

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth,trim={0.25cm 0 0cm 0}]{figures/periode.pdf}
\caption{Our calculated posterior probability to constrain the period of \planete using transit timings from \textit{K2} and \tess. We tested discrete periods from $38-60$\,days and find the most likely period to be 45.003~days. The 2:1 resonance (48.28~days) with \planetb is plotted as the dashed vertical line.} \label{fig:period_e}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth,trim={0.25cm 0 0cm 0}]{static/periode.pdf}
\caption{Our calculated posterior probability to constrain the period of \planete using transit timings from \textit{K2} and \tess. We tested discrete periods from $38-60$\,days and find the most likely period to be 45.003~days. The 2:1 resonance (48.28~days) with \planetb is plotted as the dashed vertical line. \href{https://github.com/afeinstein20/v1298tau_tess/blob/main/notebooks/V1298Tau_e.py}{\github}} \label{fig:period_e}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
